To Do List

### 2018-09-21 ToDo.Rmd
updates

* Finish TFBS models
+ Include column for feature table for why a feature was excluded
+ Use tables instead of barplots for performance metrics
+ class imbalance barplot unnecessary, put in words
* clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
* put tad in boundary before tad not in boundary for class imbalance table
* include venn diagram of selected features
* create a heat map for AIC values from commonly selected features
+ look at chromosome specific models and compare
* look at different resolutions (talk with john)
+ look at other type of transformation (inverse sine transformation)

>>>>

* Finish TFBS models
+ Include column for feature table for why a feature was excluded
+ Use tables instead of barplots for performance metrics
+ class imbalance barplot unnecessary, put in words
* clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
* put tad in boundary before tad not in boundary for class imbalance table
+ include venn diagram of selected features
* create a heat map for AIC values from commonly selected features
+ look at chromosome specific models and compare
* look at different resolutions (talk with john)
+ look at other type of transformation (inverse sine transformation)

## 09/19/18

+ split feature list into distance then counts
* run mlr/lasso without distances to compare with mourad
* find out how to obtain consensus tree from random forest
+ do we need distance?
+ look at models with just counts vs just distance; compare
